\vskip-0.6in \Large Political Uncertainty

### 2016-01-25 GS-extension.tex
add guidance at top of numerical results
correct wrong assumption about one non-neg bribe case

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		=
						  (-1)\cdot (-1) \cdot (-1)
			\left|\begin{array}{ccc}
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| =
		\]
		\[
		  (-1) \cdot (-1)
			\left|\begin{array}{cc}	
			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
		\]
		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
			\begin{itemize}
				\item This boils down to $\left(e^{-X} - 1\right) < 0$
				\item Implies $X > 0$
				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
			\end{itemize}
		\item \textbf{Why does $b(0)$ have to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$?}
		\item Can write out SOC (just after equation 33) and FOC, sub together to get
			\[
			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
			\]
			Not sure what this means
	\end{itemize}

\newpage
\subsection{Numerical Results}	
For all of these, $\beta = 1$ and there are three legislators with $b\in\left\{-\frac{1}{2},0,\frac{1}{2}\right\}$.

>>>>

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		=
						  (-1)\cdot (-1) \cdot (-1)
			\left|\begin{array}{ccc}
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| =
		\]
		\[
		  (-1) \cdot (-1)
			\left|\begin{array}{cc}	
			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
		\]
		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
			\begin{itemize}
				\item This boils down to $\left(e^{-X} - 1\right) < 0$
				\item Implies $X > 0$
				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
			\end{itemize}
		\item It is NOT the case that $b(0)$ has to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$. In fact, it seems in numerical examples that this does \textit{not} happen.
			\begin{itemize}
				\item However, I do see that this existence of the one non-negative bribe is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or WB = 9.
			\end{itemize}
		\item Can write out SOC (just after equation 33) and FOC, sub together to get
			\[
			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
			\]
			Not sure what this means
	\end{itemize}

\newpage
\subsection{Numerical Results}	
For all of these, $\beta = 1$ and there are three legislators with $b\in\left\{-\frac{1}{2},0,\frac{1}{2}\right\}$.
\begin{itemize}
	\item Below, the column headings are $v(z)$ before the bribe.
	\item That is, from left to right, $-Z,-Y,-X$.
\end{itemize}
